\documentclass{article}
\title{\bf{Litany of Memory}}
\author{Nicholas Malaya} \date{}

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Statistics
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Statistics}

Central Limit Theorem: a sufficiently large number of independent random variables, 
each with finite mean and variance, will be approximately normally distributed
\newline
\newline

\emph{aleatoric} uncertainty -- uncertainty generated from randomness
\newline
\newline
\emph{epistemic} uncertainty -- uncertainty generated from lack of knowledge
\newline
\newline

From the definition of conditional probability:
\begin{equation}
  P(A|B) = \frac{P(A \cap B) }{P(B)}
\end{equation}
We can derive Bayes:
\begin{equation}
  P(H|D) = \frac{P(D|H) P(H) }{P(D)}
\end{equation}
Let's say you heard a friend was talking to a person with long hair. Calculate probability of this person being a woman.

\begin{center}
\line(1,0){250}
\end{center}

Chebyshev Inequality:
\begin{equation}
  Pr(|x-\mu| \ge \epsilon) \le \frac{\sigma^2}{\epsilon^2}
\end{equation}

\begin{center}
\line(1,0){250}
\end{center}

Correlation:
\begin{equation}
  \rho_{x,y} = \frac{E[(x-\mu_x)(y-\mu_y)]}{\sigma_x \sigma_y}
\end{equation}

Uncertainty estimates
10 samples $\approx$ 30\%
1000 samples $\approx$ 3\%
one million samples $\approx$ 0.1\%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Mathematics
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Mathematics}
Divergence Theorem:
\begin{equation}
  \int_{S}{\bf A}\cdot d{\bf S}=\int_{V}(\nabla \cdot {\bf A})dV
\end{equation}
\newline
\newline
\begin{equation}
  Au_{xx} + Bu_{xy} + Cu_{yy} + ... = 0
\end{equation}
\newline
\newline
Hyperbolic Differential Equation: $B^2-4AC > 0$ (Wave equation, supersonic fluid)
\newline
\newline
Parabolic Differential Equation: $B^2-4AC = 0$. (Heat Diffusion,Black Sholes)
\newline
\newline
Elliptic Differential Equation: $B^2-4AC < 0$. (Laplace's equation, Incompressible Fluid)
\newline
\newline
Fourier Transform:
\begin{equation}
  f(k)dk = \int^{\infty}_{-\infty} f(x)e^{-i2\pi x k}dx
\end{equation}
Discrete Fourier Transform:
\begin{equation}
  f_k = \sum^{N-1}_{n=0} f_x e^{\frac{-i2\pi}{N} k n}
\end{equation}

Condition Number: 
\begin{equation}
  \kappa(x) = ||A|| ||A^{-1}||
\end{equation}

Taylor Series:
\begin{equation}
  f(x) \approx f(a) + \frac{f'(a)}{1!}(x-a) + \frac{f''(a)}{2!}(x-a)^2 + \frac{f^3(a)}{3!}(x-a)^3
\end{equation}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Computation
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Computation}

A one billion processor computer with today's technology would consume more than a gigawatt of electricity. 
That is more than .1\% of the total US grid.
Most american utility plants produce less than four gigawatts of electricity.
\newline
\newline
Blue Waters will require 15 megawatts.
\newline
\newline
Longhorn is the big memory TACC machine.
\newline
\newline
$4096^3 \approx 1.5$ Petabyte file.
$1024^3 \approx 25$ GB file.
$512^3 \approx   3$ GB file.
$128^3 \approx  50$ Megabyte file.
\newline
\newline
Gaussian Elimination is $O(n^3)$
\newline
\newline
Iterative techniques can converge in $O(n)$ steps.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Fluid Dynamics
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Fluid Dynamics}
%\begin{equation}
%  \frac{d}{dt}\int_{\Omega(t)} T(x,t) dV = \int_{\Omega} \frac{\partial}{\partial t} T dV + \int_{\partial \Omega} \hat n \cdot w T dA = \int_{\Omega}\frac%{\partial}{\partial t} T + \nabla \cdot w T dV
%\end{equation}
%\newline
%\newline
Friction Velocity
\begin{equation}
  u_\tau = \sqrt{\frac{\tau_w}{\rho}}
\end{equation}
\newline
\newline
The momentum thickness is transverse distance by which the boundary should be displaced to compensate for the reduction in momentum of the flowing fluid on account of boundary layer formation. 
\begin{equation}
  \theta = \int^\infty_0 \frac{u(y)}{u_0}(1-\frac{u(y)}{u_0})dy
\end{equation}
\newline
\newline
The reynolds stress tensor is the stress in a fluid due to the random turbulent fluctuations in the fluid momentum:
\begin{equation}
  \rho \overline{u'_i u'_j}
\end{equation}
\newline
\newline
Drag equation: 
\begin{equation}
  F_D = \frac{1}{2}\rho v^2 C_D A
\end{equation}
\newline
\newline
Bernoulli 
\begin{equation}
  \frac{v^2}{2}+gz+\frac{p}{\rho}=constant
\end{equation}
\newline
Assume: steady state, no friction, constant density, points are on streamlines
\newline
\newline
We advance the non-linear terms explicitly. The linear terms
implicitly. The linear terms are the viscous operator. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Combustion
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Combustion}

Rich mixture: more fuel
\newline
\newline

Lean mixture: more air



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Thermodynamics
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Thermodynamics}

Adiabatic: no net heat transfer to or from the working fluid. (Insulated Walls, process has short time scale, etc.)
\newline
\newline
Ideal gas undergoing a reversable adiabatic process: 
\begin{equation}
  PV^{\gamma} = c
\end{equation}
Where $\gamma$ is the ratio of the specific heats
\begin{equation}
  \gamma = \frac{C_p}{C_v}
\end{equation}
With $C_p$ specific heat for constant pressure, and $C_v$ constant volume.

Arrhenius Equation:
\begin{equation} 
 k = Ae^{-E_a/RT}
\end{equation}
The rate constant has units of inverse time $[\frac{1}{s}]$.
\newline
\newline
Fick's law:
\begin{equation} 
 J = -D\frac{\partial \phi}{\partial x_i}
\end{equation}
J is the diffusion flux. 
\newline
\newline
Mass Concentration
\begin{equation} 
  \rho_i = m_i / V 
\end{equation}

Mole Fraction
\begin{equation} 
  x_i = n_i / n_{tot}
\end{equation}

Mass fraction
\begin{equation} 
 \omega_i = \rho_i / \rho
\end{equation}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Dimensionless Numbers
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Dimensionless Numbers}
Schmidt Number:
\begin{equation}
  Sc = \frac{\nu}{D}
\end{equation}
The ratio of momentum diffusivity (viscosity) and mass diffusivity
\newline
\newline
Damkohler Number
\begin{equation}
  Da = \frac{\textrm{fluid time}}{\textrm{chemical reaction time}}
\end{equation}
\newline
\newline
Knudson Number
\begin{equation}
  Kn = \frac{\lambda}{L}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Random Facts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Random Facts}
The universe is roughly $2.6 e^{26}$ meters in size
\newline
\newline
The plank length is is roughly $1.6 e^{-35} $ meters

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        electronics
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Electronics}

metal–oxide–semiconductor field-effect transistor (MOSFET, MOS-FET, or
MOS FET) is a transistor used for amplifying or switching electronic
signals. 
\newline
\newline
CMOS circuits use a combination of p-type and n-type
metal–oxide–semiconductor field-effect transistors (MOSFETs) to
implement logic gates and other digital circuits 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Language
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Language}
e.g. means ``in other words''
\newline
\newline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Finance
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Finance}
EBIDA -- earnings before interest, taxes, and amortization
\newline
\newline
GAAP  -- General Accepted Accounting Principles
\newline
\newline
IFRS  -- International Financial Reporting Standards
\newline
\newline
Put option -- right to sell an asset. (think price decreasing)
\newline
\newline
Call option -- right to buy an asset. (think price increasing)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        finis
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Finis}
Amat victoria curam -- ``Victory Loves careful preparation''
\newline
\newline
nil nisi bonum -- ``nothing but good''
\newline
\newline
nec fas est proprius Mortali attingere Divos -- ``It is not lawful for mortals to approach divinity closer than this''

\end{document}
